---
title: "Module # 9 Visualization in R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
knitr::opts_chunk$set(message = FALSE, comment = NA, warning = FALSE)
library(ggplot2)
library(ggmap)
library(gridExtra)
library(ggiraph)
library(plotly)
```

For this assignment, I have chosen to use my own data obtained from my job as a restaurant delivery driver. The dataset contains a total of `r nrow(df)` observations and the variables I chose to record are:

Date | Address | Order Amount | Tip Amount | Age | Time | Tip Included | Dog Owner 


```{r}
df = read.csv("C:/Users/adamw/Documents/Data Textmining/Delivery Data/Delivery Data - Sheet1 (1).csv")

```

For the first visualization I plotted all of my orders on a map and filled them in by tip percentage of total order.

```{r}
df$Address = as.character(df$Address)
register_google(key = "AIzaSyDLHeQB3O4nhAMtQJLRVKpGohvk5FPB3dg")
df$latlon = geocode(df$Address)
df$TipPercentage = df$TipAmt/df$OrderAmt
df$Gender = as.factor(df$Gender)

dfdog = subset(df, Dog == "Yes")
dfnodog = subset(df, Dog == "No")

dfmale = subset(df, Gender == "Male")
dffemale = subset(df, Gender == "Female")
```

```{r}
tampa.map <-get_map(c(-82.492610,27.914840), zoom = 12,maptype = "terrain")

mapSimple <- ggmap(tampa.map)

df = subset(df, df$TipPercentage <= .35)

mapSimple+geom_point(data = df, aes(x = latlon$lon, y = latlon$lat, color = TipPercentage,), size = 3, alpha = 6/10)+scale_color_gradient(low="blue", high="red",  limits=c(0,.35))+ggtitle("Tampa Delivery Map")
```

The second visualization is a scatterplot of the same variables, however this one is colored by gender.

```{r}
ggplot(df, aes(df$OrderAmt, df$TipPercentage, color = df$Gender))+geom_jitter()+ xlab("Order Amount")+ylab("Tip Percentage")+labs(color = "Gender")+ggtitle("Percentage of Tip Based on Total Order")+
  geom_smooth(method = "lm")
```

The last visualization plots the number of orders placed throughout the evening.

```{r}
f = subset(df, df$TipPercentage < .35)
df$Time = as.POSIXct(df$Time,format="%H:%M:%S")

dfdog = subset(df, Dog == "Yes")
dfnodog = subset(df, Dog == "No")
dfdog$Time = as.POSIXct(dfdog$Time,format="%H:%M:%S")
dfnodog$Time = as.POSIXct(dfnodog$Time,format="%H:%M:%S")

dfmale$Time = as.POSIXct(dfmale$Time,format="%H:%M:%S")
dffemale$Time = as.POSIXct(dffemale$Time,format="%H:%M:%S")

#df$Time = as.Date(df$Time)
#df$Time = format(as.POSIXct(df$Time,format='%m/%d/%Y %H:%M:%S'),format='%H:%M')

ggplot(df, aes(x=Time, fill= Gender))+geom_bar()+theme(axis.text.x = element_text(size = 12,angle = 80))+scale_x_datetime(date_breaks = "30 min", date_labels = "%H:%M")+ylab("Number of Orders")+ggtitle("Number of Orders Based on Time of Day")+xlab("Time (PM)")
```

